Fail Faster

### 2025-03-20 paper/paper.tex
nit

%\jwc{NOTE: we should test generator speed across both languages, but speed -> bugfinding ability in only OCaml.}
%\jwc{
%  Baseline generators to test speed in both languages:
%  \begin{itemize}
%    \item Single int
%    \item Pair of ints, constrained
%    \item List of ints without bind (use map): lots of sampling, minimal binds.
%    \item Unableled Trees of a fixed size (no weighted union) minimal sampling, lots of binds.
%  \end{itemize}
%}
\subsection{Benchmarking bug-finding speed}
To answer \textbf{RQ2}, we evaluate the bug-finding speed of our BST and STLC
case studies using Etna, a platform for assessing and comparing PBT techniques. 
Etna allows users to measure the effectiveness of different generator
implementations by injecting bugs into the system under test and recording the
time taken for a relevant property to fail in response. For example, in a tree
with an ordering property, a bug injection might consist of inserting a value
into the tree that violates that ordering. Each case study includes a diverse
set of \textit{tasks}, where a task consists of a specific bug-property pair
designed to test different aspects of the system (e.g., BST includes tasks that
test insertion, deletion, and union operations on binary search trees). 
In particular, BST has 37 tasks, and STLC has 20. Strategies for BST and STLC 
are implemented in 
\camlname; they are unchanged from their description in \secref{subsection:benchmarking}.\footnote{Etna does 
not support Scala, so we were unable to test \scalaname's bug-finding speed in Etna, but we see no reason
we see no reason our results in this section would not extend to \scalaname.}

>>>>

%\jwc{NOTE: we should test generator speed across both languages, but speed -> bugfinding ability in only OCaml.}
%\jwc{
%  Baseline generators to test speed in both languages:
%  \begin{itemize}
%    \item Single int
%    \item Pair of ints, constrained
%    \item List of ints without bind (use map): lots of sampling, minimal binds.
%    \item Unableled Trees of a fixed size (no weighted union) minimal sampling, lots of binds.
%  \end{itemize}
%}
\subsection{Benchmarking bug-finding speed}
To answer \textbf{RQ2}, we evaluate the bug-finding speed of our BST and STLC
case studies using Etna, a platform for assessing and comparing PBT techniques. 
Etna allows users to measure the effectiveness of different generator
implementations by injecting bugs into the system under test and recording the
time taken for a relevant property to fail in response. For example, in a tree
with an ordering property, a bug injection might consist of inserting a value
into the tree that violates that ordering. Each case study includes a diverse
set of \textit{tasks}, where a task consists of a specific bug-property pair
designed to test different aspects of the system (e.g., BST includes tasks that
test insertion, deletion, and union operations on binary search trees). 
In particular, BST has 37 tasks, and STLC has 20. Strategies for BST and STLC 
are implemented in 
\camlname; they are unchanged from their description in \secref{subsection:benchmarking}.\footnote{Etna does 
not support Scala, so we were unable to test \scalaname's bug-finding speed in Etna, but we
we see no reason our results in this section would not extend to \scalaname.}
